---
name: Katie
surname: Von Holzen
position: "Akademische Rätin"
address: "Emil-Figge Str. 50, 44227 Dortmund, Germany, Tel: (+49)231 755-2850"
profilepic: "./img/katie_headshot.jpg"
www: Kvonholzen.github.io
email: katie.vonholzen@tu-dortmund.de
github: Kvonholzen
twitter: KatieVonHolzen
date: "`r format(Sys.time(), '%B %Y')`"
docname: "Teaching and Mentorship"
output: vitae::hyndman

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

current_dir <- getwd()
current_dir <- gsub("specialized_CVs/Leuphana_DevPsych", "", current_dir)


knitr::opts_knit$set(root.dir = current_dir)

# hyndman

library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)
library(tidyverse)
library(grid)
library(gridExtra)
library(gtable)
#library(RefManageR)

# bib <- ReadBib("Publications.bib")
# print(bib)


```


# Courses Taught


```{r}

teaching_data <- read.csv(file = "data/teaching.csv", header = T)


teaching_data <- sapply(teaching_data, as.character)
teaching_data[is.na(teaching_data)] <- " "

teaching_data <- as.data.frame(teaching_data)


```


## Seminars


```{r}

seminar_data <- subset(teaching_data, Type == "Seminar")


seminar_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Desc,
    with = "",
    why = Evaluation
  )

```


## Lecture-based Courses

```{r}

lecture_data <- subset(teaching_data, Type == "Lecture")

lecture_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Desc,
    with = "",
    why = Evaluation
  )

```


## Tutorials

*I've written a suite of Tutorials available on my website (https://kvonholzen.github.io/Tutorials.html) for creating experiments in Open Sesame, analyzing data in R, working in Praat, and preprocessing EEG/ERP data in EEGlab/ERPlab. I've also created a tutorial for analyzing eyetracking data with R (https://bookdown.org/katie_m_vonholzen/Eyetracking_Statistical_Analysis_Tutorial/)*

```{r}

tutorial_data <- subset(teaching_data, Type == "Tutorial")


tutorial_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    with = "",
    why = Desc
  )

```


# Students Mentored


```{r}

student_data <- read.csv(file = "data/students.csv", header = T)

student_data <- sapply(student_data, as.character)
student_data[is.na(student_data)] <- " "

student_data <- as.data.frame(student_data)

```

## Doctoral students

```{r}

phd_data <- subset(student_data, Type == "PhD")


phd_data %>%
  detailed_entries(
    what = Title,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Person,
    with = Institution
  )


```

## Master students

```{r}

master_data <- subset(student_data, Type == "Master")


master_data %>%
  detailed_entries(
    what = Title,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Person,
    with = Institution
  )


```


## Bachelor students

```{r}

bachelor_data <- subset(student_data, Type == "Bachelor")


bachelor_data %>%
  detailed_entries(
    what = Title,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Person,
    with = Institution
  )

```

## Internships and project assistantships

```{r}

intern_data <- subset(student_data, Type == "Intern")

intern_data %>%
  detailed_entries(
    what = Title,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Person,
    with = Institution
  )


# - Sofia Carrion, 2017
# - Elisa Moulin, 2015-2016
# - Jeanne Charoy, 2015
# - Marion Lafargue, 2014-2015 

# - Safyya Larinouna, 2016
# - Henry Cheng, 2014 


# *Spoken word perception in L1 and L2: An ERP study of the influence of speaker, gender, frequency, and repetition*, Georg-August-Universität Göttingen, 2012
# - Agniezska Leszczynska

```


