---
name: Katie
surname: Von Holzen
position: "Lecturer and Researcher"
address: "Hagenring 22, 38106 Braunschweig, Germany"
profilepic: "./img/katie_headshot.jpg"
pronouns: she/her
www: Kvonholzen.github.io
email: katie.m.vonholzen@gmail.com
phone: +49 172 52 86 485
github: Kvonholzen
twitter: KatieVonHolzen
date: "`r format(Sys.time(), '%B %Y')`"
docname: "Publication List"
output:
  vitae::hyndman:
    latex_engine: xelatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

# hyndman

library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)
library(tidyverse)
library(grid)
library(gridExtra)
library(gtable)
#library(RefManageR)

# bib <- ReadBib("Publications.bib")
# print(bib)

```

# Published peer-reviewed papers

```{r}

# apostrophe's need to be given as $'$
# remove papers that are under review, revision, or accepted
notpublished = c("IniSegPhonotactics", "IniSegLexTransparency",
                 "SarahLWLpilot",
                 "ChineseWordLearning",
                 "AdultIDSADS",
                 "ROFFS",
                 "MB5")

bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "article-journal") %>%
  filter(!id %in% notpublished) %>%
  #filter(id != "MB5" & id != "AdultIDSADS") %>%
  arrange(desc(issued), author)


```

# Manuscripts accepted

```{r}
# 



bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "article-journal") %>%
  filter(id == "MB5") %>%
  arrange(author)

```


# Manuscripts under revision or review

```{r}

notpublished = c("AdultIDSADS",
                 "ROFFS")

bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "article-journal") %>%
  filter(id %in% notpublished) %>%
  #filter(id != "MB5" & id != "AdultIDSADS") %>%
  arrange(author)

```

# Manuscripts in preparation

```{r}

# apostrophe's need to be given as $'$
# remove papers that are under review, revision, or accepted
notpublished = c("IniSegPhonotactics", "IniSegLexTransparency",
                 "SarahLWLpilot",
                 "ChineseWordLearning")

bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "article-journal") %>%
  filter(id %in% notpublished) %>%
  #filter(id != "MB5" & id != "AdultIDSADS") %>%
  arrange(author)


```


# Chapters in Books

```{r}
bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "chapter") %>%
  arrange(desc(issued), author)

```

# Peer-Reviewed Conference Proceedings

```{r}
bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "paper-conference") %>%
  arrange(desc(issued), author)
```

# Open Data

The entire set of materials, data, and analysis scripts for these manuscripts are hosted by the Open Science Framework.

```{r}

be <- bibliography_entries("data/Publications.bib") %>%
  filter(id %in% "VonHolzen2021" | id %in% "AdultIDSADS" | id %in% "CVaccent" | id %in% "ROFFS") %>%
  arrange(author)


```

# PhD Thesis

```{r}
bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "thesis") %>%
  arrange(desc(issued), author)

```


# Invited Talks and Conference Activity

## Invited Talks


```{r}

bibliography_entries("data/Presentations.bib") %>%
  filter(str_detect(id, "^i"))%>%
  arrange(desc(issued), author)

```


## Conference Talks


```{r}
bibliography_entries("data/Presentations.bib") %>%
  filter(str_detect(id, "^t"))%>%
  arrange(desc(issued), author)
```



## Conference Posters


```{r}

bibliography_entries("data/Presentations.bib") %>%
  filter(str_detect(id, "^p"))%>%
  arrange(desc(issued), author)

```