---
name: Katie
surname: Von Holzen
position: "Lecturer and Researcher"
address: "Hagenring 22, 38106 Braunschweig, Germany"
profilepic: "./img/katie_headshot.jpg"
pronouns: she/her
www: Kvonholzen.github.io
email: katie.m.vonholzen@gmail.com
phone: +49 172 52 86 485
github: Kvonholzen
twitter: KatieVonHolzen
date: "`r format(Sys.time(), '%B %Y')`"
docname: "Curriculum Vitae"
output:
  vitae::hyndman:
    latex_engine: xelatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

# hyndman

library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)
library(tidyverse)
library(grid)
library(gridExtra)
library(gtable)
#library(RefManageR)

# bib <- ReadBib("Publications.bib")
# print(bib)

```

# Research Areas


```{r}

research_area <- read.csv(file = "data/research_areas_AppliedLing.csv", header = T)

research_area <- research_area %>%
  group_by(area) %>%
  dplyr::mutate(detail_list = paste0(detail, collapse = "; "))

research_area <- unique(research_area[,c("area", "detail_list")])


research_area %>%
  detailed_entries(
    what = detail_list,
    when = area
  )



```


# Employment

```{r}


employ_data <- read.csv(file = "data/employment.csv", header = T)


employ_data %>%
  detailed_entries(
    what = Position,
    when = glue::glue("{Start_Year} - {End_Year}"),
    where = Institution,
    with = Supervisor
  )

```

# Education

```{r}

# needed to add " to get special characters to read in properly
edu_data <- read.csv(file = "data/education.csv", header = T)
#edu_data <- read.csv(file = "data/education.csv", header = T)

edu_data %>%
  detailed_entries(
    what = Degree,
    when = glue::glue("{Start_Year} - {End_Year}"),
    where = Institution,
    with = ""
  )


```

# Awards

```{r}

awards_data <- read.csv(file = "data/awards.csv", header = T)

awards_data <- subset(awards_data, Year != 2009)

awards_data %>%
  detailed_entries(
    what = Name,
    when = Year,
    where = Desc,
    with = Amount
  )

```




# Professional Memberships

```{r}

prof_member <- read.csv(file = "data/memberships.csv", header = T)

prof_member %>%
detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year} - {End_Year}"),
    where = "",
    with = "")


```

# Research Cooperations

Please find below a summary of my ongoing research cooperations that are not yet reflected in my publication record.

- ManyBabies-AtHome: Sho Tsuji (École normale supérieure, France; University of Toyko, Japan), Rhodri Cusack (Trinity College Dublin, Ireland), Lorijn Zaadnoordijk (Trinity College Dublin, Ireland)
- ManyBabies-AtHome Looking-While-Listening Project: Eon-Suk Ko (Chosun University, South Korea), Julian Mayor (University of Oslo, Norway), Martin Zettersten (University of California - San Diego, USA), Silvia Benavides Varela (Padua University, Italy), Barbara Pomiechowska (University of Birmingham, UK), Anna Exner (Ruhr University Bochum, Germany)
- Novelty Preference Meta-Analysis: Martin Zettersten (University of California - San Diego, USA), Anjie Cao (Stanford University, USA)
- How noise in the home environment impacts children's development: Rochelle Newman (University of Maryland, USA), Rachel Romeo (University of Maryland, USA), Meg Cychosz (University of California - Los Angeles, USA)


# Service

## Institutional Service

```{r}

inst_service <- read.csv(file = "data/service.csv", header = T)

inst_service <- sapply(inst_service, as.character)
inst_service[is.na(inst_service)] <- " "

inst_service <- as.data.frame(inst_service)


inst_service %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Institution,
    with = ""
  )


```

## Professional Service

For a complete record of my peer-review service, view my Web of Science Peer Review Profile (https://www.webofscience.com/wos/author/record/1483321), which includes, among others, reviews at the journals Child Development, Language and Speech, and Language Acquisition. I have reviewed for international workshops and conferences, including the International Congress of Infant Studies, the International Association for the Study of Child Language, the International Symposium on Bilingualism (Area Co-Chair: Infant and Child Development).


```{r}
### Conference Review
# 
# - International Congress of Infant Studies (ICIS) Conference (2020), Glasgow, UK
# - International Association for the Study of Child Language (IASCL) Conference (2020), Philadelphia, PA, USA
# - CCERBAL Conference: Bilingual from Birth: Process, Pedagogy and Policy (2016). Ottawa, Canada
# - International Workshop on Bilingualism and Cognitive Control (2013). Jagiellonian University, Krakow, Poland
# - International Workshop: “Bilingual and Multilingual Interaction” ESRC Centre for Research on Bilingualism (2012), Bangor, Wales

```



# Languages

- English, native
- German, fluent (C1)
- French, proficient (B1)







