---
title: 'MB AtHome: LWL stimuli AoA Calculation'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

# Target Word Choice Algorithm

This script is designed to aid the MB-AH LWL project researchers in choosing target words to test in each language. It relies on the age of acquisition data calculated by Wordbank in available languages. 

We focus first on stimuli selection for infants under 18 months. For each language, we would like to select 12 words, consisting of 8 nouns (4 pairs of 2) and 4 verbs (2 pairs of 2). This approach assumes that words will vary across languages, while strictly controlling for estimated age of acquisition (AoA). The measure of AoA that we use is the age at which 50% of children are estimated to understand the word. It will also control for semantic categories, focusing on the categories "body_parts" and "food_drink" for nouns (following Bergelson & Swingley, 2012). *any similar-ish restrictions for verbs?*

For the nouns:

* 4 of the nouns should be acquired early (AoA around 12 months)
    + 2 nouns should come from the category "body_parts"
    + 2 nouns should come from the category "food_drink"
* 4 of the nouns should be acquired late (AoA around 18 months)
    + 2 nouns should come from the category "body_parts"
    + 2 nouns should come from the category "food_drink"

For the verbs:

* 2 of the verbs should be acquired early (AoA around 12 months)
* 2 of the verbs should be acquired early (AoA around 18 months)

**If only production data is available:** The above AoA values should be based on comprehension data. If only production data is available, then take an AoA of around 18 months for early AoA and 24 months for late AoA

Language specific constraints concerning target-distractor pairs:

* Nouns should be paired with nouns and verbs paired with verbs
* Early nouns should be paired together, late nouns should be paired together (e.g. early body_parts paired with early food_drink)
* Early verbs should be paired together, late verbs should be paired together
* Pairs should have the same grammatical gender if your language uses determiners that mark grammatical gender (e.g., la/le in French); 
* Pairs should not start with the same phoneme

**But I've got too many words to choose from!** As you can see below, each word decision is accompanied by a justification for choosing those particular words, beyond the constraints we've provided for target word choice. Use your best judgement and document with detail how you reached your decision.

# Example: American English

To determine the AoA of words and facilitate our choice of target words, we can query the [Wordbank](http://wordbank.stanford.edu/) database. First we load the packages we'll need. 

```{r packages}

# R version 4.1.0 (2021-05-18) -- "Camp Pontanezen"

library(wordbankr)
library(dplyr)
library(tidyr)
library(purrr)
library(stringi)
library(kableExtra)

```

Then, we will want to set the language we'd like to choose stimuli for. We can use the "get_instruments()" function from the wordbankr package. The options are:

```{r echo = FALSE}

gi <- get_instruments()

gi %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```

We'll start with American English and we set the variable "wordbank_lang" to "English (American)", as this is how this language is defined in wordbankr.

```{r English_1}

wordbank_lang <- "English (American)"


```

Next, we find out the AoA for comprehension and production for nouns from the body_part and food_drink categories as well as for verbs. The wordbank package will do most of the heavy lifting here and we'll be using the "fit_aoa" function. [You can read more here.](https://cran.r-project.org/web/packages/wordbankr/vignettes/wordbankr.html#advanced-functionality-age-of-acquisition) This script will return "aoa.m", which is a summary of the youngest reported AoA for unterstanding and producing. You can download the wordbank.R file from the script folder in this repository or .

```{r English_2}

source("scripts/wordbank.R")

```

## Choosing the Nouns

### Body Parts

We can examine the potential noun target words from the body parts category. They're saved in the object "body_parts". Here are our potential words, ordered by the AoA for comprehension (Wordbank_AoA_understands):


```{r echo = FALSE}

body_parts %>% 
  arrange(Wordbank_AoA_understands)  %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```
#### Early AoA

There are several potential words with AoA's around 12 months: nose, eye, foot, hair, and mouth. Hair can be rather difficult to represent in an image and if we look at the words that are available for the late AoA, eye and foot are different enough from the potential words there to limit confusion.

Words chosen: **eye** and **foot**

#### Late AoA

There are several potential words with AoA's around 18 months, perhaps the most image-able of these are: arm, finger, toe, tongue, and leg. If we look at the words that are available for the early AoA, finger and tongue are different enough from the potential words there to limit confusion.

Words chosen: **finger** and **tongue**



### Food Drink

We can examine the potential noun target words from the food/drink category. They're saved in the object "food_drink". Here are our potential words, ordered by the AoA for comprehension (Wordbank_AoA_understands):


```{r echo = FALSE}

food_drink %>% 
  arrange(Wordbank_AoA_understands)  %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```


#### Early AoA

There are several potential words with AoA's around 12 months: banana, juice, milk, and cookie. Cookies can take many different forms and we don't want to choose both juice and milk, because they are similar to each other. Juice has a slightly lower production AoA, so we choose this one.

Words chosen: **banana** and **juice**


#### Late AoA

There are several potential words with AoA's around 18 months: carrots, egg, pasta, peas, and pizza. Pizza and egg both have lower production AoAs and are quite imageable.

Words chosen: **pizza** and **egg**


## Choosing the Verbs

We can examine the potential verb target words. They're saved in the object "verbs". Here are our potential words, ordered by the AoA for comprehension (Wordbank_AoA_understands):


```{r echo = FALSE}

verbs %>% 
  arrange(Wordbank_AoA_understands)  %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```


#### Early AoA

There are several potential words with AoA's around 12 months that are easily image-able: kiss, drink, eat, and hug. Eat has a lower lower production AoA, than drink and kiss is more easily image-able than hug.

Words chosen: **eat** and **kiss**


#### Late AoA

There are a couple words with AoA's around 18 months that are easily image-able: smile, sit, and draw. Both smile and sit start with the same onset, so we choose smile, since it has the lower AoA.

Words chosen: **smile** and **draw**






## Target-Distractor pairs

We also need to choose target-distractor pairs that follow the constraints we've set. They are:

* Nouns should be paired with nouns and verbs paired with verbs
* Early nouns should be paired together, late nouns should be paired together (e.g. early body_parts paired with early food_drink)
* Early verbs should be paired together, late verbs should be paired together
* Pairs should have the same grammatical gender if your language uses determiners that mark grammatical gender (e.g., la/le in French); 
* Pairs should not start with the same phoneme

### Nouns

#### Early AoA:
* body_parts: eye, foot
* food_drink: banana, juice

English doesn't have grammatical gender and none of these words start with the same phoneme. So, we could pair these together however we wish. Here are the pairs chosen:

* banana - eye
* juice - foot

#### Late AoA:
* body_parts: finger, tongue
* food_drink: pizza, egg

English doesn't have grammatical gender and none of these words start with the same phoneme. So, we could pair these together however we wish. Here are the pairs chosen:

* egg - finger
* pizza - tongue

### Verbs

Here the pairing is straightforward, since there are only 2 early AOA verbs and 2 late AoA verbs:

#### Early AoA:
* eat - kiss

#### Late AoA:
* smile - draw

## Final List

* banana - eye
* juice - foot
* egg - finger
* pizza - tongue
* eat - kiss
* smile - draw


# Example: German

American English doesn't use grammatical gender, which is an additional constraint in our word choice. To illustrate how this will work in choosing target words, we work through a different example, German. German also doesn't have CDI data for comprehension available in the Wordbank database. So, instead of AoAs of 12 and 18 for ealy and late, we'll use 18 and 24, to approximate differences in when these words are likely understood.

```{r German}

wordbank_lang <- "German"

source("scripts/wordbank.R")

```


## Choosing the Nouns

### Body Parts

```{r echo = FALSE}

body_parts %>% 
  arrange(Wordbank_AoA_understands)  %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```

#### Early AoA

There are several potential words with AoA's around 18 months that are easily image-able: Nase (nose), Ohr (ear), Füße (feet), Auge (eye), Bein (leg), Mund (mouth), Arm (arm). Of these, Nase and Ohr have the lowest AoAs, but if we skip ahead to food_drink, we see that we're limited in the gender of our choices. So, we choose Mund, as it has masculine gender, and Ohr, as it has neuter gender.

Words chosen: **Mund** and **Ohr**

#### Late AoA

There are several potential words with AoA's around 24 months that are easily image-able: Finger (finger), Knie (knee), Zeh (toe), Zunge (tongue). Of these, Finger and Knie have the lowest AoAs, but if we skip ahead to food_drink, we see that we're limited in the gender of our choices. So we choose Zunge instead of Knie, as it has feminine gender.

Words chosen: **Finger** and **Zunge**

### Food Drink

```{r echo = FALSE}

food_drink %>% 
  arrange(Wordbank_AoA_understands)  %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```


#### Early AoA

There are several potential words with AoA's around 18 months: Apfel (apple), Eis (ice cream), and Eier (eggs). Ice cream can take many different forms, so we choose Apfel and Eier. But, since Eier is a plural form and we need to match the neuter Ohr, we take the singular form Ei (egg).

Words chosen: **Apfel** and **Ei**

#### Late AoA

There are several potential words with AoA's around 24 months: Butter (butter), Saft (juice), Pizza (pizza) and Tomate (tomato). Pizza and Saft are perhaps the easiest of these to image.

Words chosen: **Saft** and **Pizza**



## Choosing the Verbs

We can examine the potential verb target words. They're saved in the object "verbs". Here are our potential words, ordered by the AoA for comprehension (Wordbank_AoA_understands):


```{r echo = FALSE}

verbs %>% 
  arrange(Wordbank_AoA_understands)  %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```


#### Early AoA

There are a couple potential words with AoA's around 18 months that are easily image-able: essen (eat), trinken (drink), and malen (draw). Trinken and essen are quite similar to one another, so we choose trinken, as it is a more regular verb.

Words chosen: **trinken** and **malen**


#### Late AoA

There are a couple words with AoA's around 24 months that are easily image-able: kissen (kiss) and sitzen (sit).

Words chosen: **kissen** and **sitzen**


## Target-Distractor pairs

### Nouns

#### Early AoA:
* body_parts: Mund (m), Ohr (n)
* food_drink: Apfel (m), Ei (n)

* Mund - Apfel
* Ohr - Ei

#### Late AoA:
* body_parts: Finger (m), Zunge (f)
* food_drink: Saft (m), Pizza (f)

* Finger - Saft
* Zunge - Pizza


### Verbs
* Early AoA: trinken, malen
* Late AoA: kissen, sitzen

* trinken - malen
* kissen - sitzen

## Final List

* Mund - Apfel
* Ohr - Ei
* Finger - Saft
* Zunge - Pizza
* trinken - malen
* kissen - sitzen

# Advanced: No Wordbank Data available

Could use private lab CDI data
or best judgement, but document it!

Coming soon: pipeline for computing AoA on private lab CDI data






