---
title: "Curriculum Vitae"
bibliography: cv/data/Publications.bib
csl: apa-cv.csl
---

----

Download my full [Curriculum Vitae](cv/K_Von_Holzen_CV.pdf) here

----

```{r setup_cv, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)
library(dplyr)
```


# Education
 
<div class = "row">
  
<div class = "col-sm-2">
<br>in progress
<br>
<br>
<br>2013
<br>
<br>
<br>2009
<br>
</div>
  
<div class = "col-lg-6">
<br>Habilitation English Linguistics
<br>TU Braunschweig, Germany
<br>
<br>Dr. rer. nat. Psychology, magna cum laude
<br>Georg-August-Universität Göttingen, Germany
<br>
<br>B.S. Psychology, summa cum laude
<br>University of Wisconsin - Green Bay, USA
</div>
</div> 
 
 
 
# Employment

<br>Wissenschaftliche Mitarbeiterin (Lecturer and Researcher)
<br>English Linguistics,
<br>Technische Universität Braunschweig, Germany
<br>Group Lead: Prof. Dr. Holger Hopp
<br>2022-present
<br>
<br>Media Coordinator
<br>International Association for the Study of Child Language (IASCL)
<br>Supervisor: Prof. Dr. Annick De Houwer
<br>2023-present
<br>
<br>Akademische Rätin (Senior Postdoc)
<br>Lehrstuhl Linguistik des Deutschen,
<br>Schwerpunkt Deutsch als Fremdsprache/Deutsch als Zweitsprache
<br>Technische Universität Dortmund, Germany
<br>Group Lead: Prof. Dr. Sarah Schimke
<br>2019-2022
<br>
<br>Postdoctoral Researcher
<br>Department of Hearing and Speech Sciences
<br>University of Maryland, USA
<br>Mentor: Dr. Rochelle Newman
<br>2017-2019
<br>
<br>Postdoctoral Researcher
<br>Speech Group, Laboratorire Psychologie de la Perception
<br>Université Paris Descartes, France
<br>Mentor: Dr. Thierry Nazzi
<br>2014-2017
<br>
<br>Scientific Staff
<br>Junior Research Group "Language Acquisition"
<br>Georg-August-Universität Göttingen, Germany
<br>Supervisor: Prof. Dr. Nivedita Mani
<br>2010-2013
<br>
<br>Summer Research Intern
<br>Kellerton Laboratory
<br>Dartmouth College, USA
<br>Supervisor: Dr. Todd Heatherton
<br>2009
<br>

# Research Areas

 * First, second and foreign-language acquisition
 * Individual learner variation
 * Accessibility and diversity
 * Open and reproducible approaches
 * Large-scale collaborations (Many Babies)
 * Cross-linguistic similarity algorithms
 * Developmental language outcomes
 * Supportive aspects of the input
 * Cross-linguistic similarity algorithms
 * Acoustic corpus analyses
 * Speech segmentation
 * Phono-lexical processing
 * Foreign speech processing
 * Word/wordform recognition
 * Consonant bias in lexical processing
 * Bilingual lexical access
 * Mispronunciation sensitivity
 * Event-Related Potentials (ERPs) 




# Peer-reviewed papers

```{r}

# apostrophe's need to be given as $'$
# remove papers that are under review, revision, or accepted
notpublished = c("IniSegPhonotactics", "IniSegLexTransparency",
                 "SarahLWLpilot",
                 "ChineseWordLearning",
                 "AdultIDSADS",
                 "ROFFS",
                 "MB5")


#easily get the keys for my published articles
pubs <- bibliography_entries("cv/data/Publications.bib") %>%
  filter(type %in% "article-journal") %>%
  filter(!id %in% notpublished) %>%
  #filter(id != "MB5" & id != "AdultIDSADS") %>%
  arrange(desc(issued), author)


#unique(pubs$id)

#unique(pubs$key)
# accepted <- bibliography_entries("cv/data/Publications.bib") %>%
#   filter(type %in% "article-journal" & issued %in% "accepted") %>%
#   arrange(desc(issued), author)

#unique(accepted$id)

```

---
nocite: |
  @Autism, @MetaAnalysis,  @VonHolzen2020, @Raneri2020, @OFallon2020, @MB1, @Basque, @VonHolzen2019, @VonHolzen2018, @Nazzi2016, @VonHolzen2014, @VonHolzen2012; @CVaccent
...


