---
title: "Teaching"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup_teaching, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)

```

----

## Resources and Materials

### QALMRI Framework

Starting with the course "Should I Buy That? Comparing Media Claims with Scientific Evidence from Brain & Behavior Research", which I taught as an [I-Series course](https://gened.umd.edu/i-series/iseries.html) to incoming freshman at the University of Maryland (and which was conceptualized by [Jared Novick](https://hesp.umd.edu/facultyprofile/novick/jared)), I began using the QALMRI Framework to guide students through reading primary, scientific articles ([Brosowsky & Parshina, 2017](https://pdfs.semanticscholar.org/3bed/03eae99d886c3c7967419d3d3cfcb132b1ee.pdf)). The QALMRI Framework stands for:

 * Q: Question
 * A: Alternatives
 * L: Logic
 * M: Methods
 * R: Results
 * I: Inferences
 
and teaches students how to identify the questions being asked in the scientific article as well as how those questions are answered and the consequences of those answers. I've since used this approach in a seminar class on bilingualism taught at the Master level at the TU Dortmund. In this class, I found it particularly helpful in preparing students to summarize existing research and create an approach to answering their own research questions (Forschungskonzept).

----

## Teaching Experience

### Lecture-based Courses

<div class = "row">
  
<div class = "col-sm-2">
<br>2018
<br>
<br>
<br>
<br>
<br>2011
<br>
<br>
<br>
<br>
</div>
  
<div class = "col-lg-6">
<br>**Should I Buy That? Comparing Media Claims with Scientific Evidence from Brain & Behavior Research**
<br>Bachelor students
<br>Department of Hearing and Speech Sciences
<br>University of Maryland
<br>
<br>**Experimental Methods for Testing Language Comprehension**
<br>Bachelor students
<br>German Department
<br>Georg-August-Universität Göttingen
<br>
</div>
</div> 


### Seminars

<div class = "row">
  
<div class = "col-sm-2">
<br>2019 - present
<br>
<br>
<br>
<br>
<br>2019 - present
<br>
<br>
<br>
<br>
<br>2012
<br>
<br>
<br>
<br>
</div>
  
<div class = "col-lg-6">
<br>**Zwei Sprachen, ein Gehirn: Bilingualismus und dessen Konsequenzen (Two Languages, One Mind: Bilingualism and its Consequences)**
<br>Master students
<br>German Department
<br>Technische Universität Dortmund
<br>
<br>**Einführung in die Sprachwissenschaft (Introduction to Linguistics)**
<br>Bachelor students
<br>German Department
<br>Technische Universität Dortmund
<br>
<br>**Language Acquisition and Processing**
<br>Bachelor students
<br>German Department
<br>Georg-August-Universität Göttingen
<br>
</div>
</div> 


### Tutorials

Some resources from these tutorials can be found under the [Tutorials](Tutorials.html) tab.

<div class = "row">
  
<div class = "col-sm-2">
<br>2017
<br>
<br>
<br>
<br>2017
<br>
<br>
<br>
<br>2016
<br>
<br>
<br>
</div>
  
<div class = "col-lg-6">
<br>**Setting up and analyzing an eye-tracking experiment: From Open Sesame to Eyelink to R**
<br>Doctoral students, postdoctoral researchers, and faculty
<br>Université Paris Descartes
<br>
<br>**Time Course Analysis in R**
<br>Doctoral students, Research Training Group 2070
<br>Georg-August-Universität Göttingen
<br>
<br>**EEG Pre-processing and Analysis Using EEGLAB and ERPLAB**
<br>Doctoral students, postdoctoral researchers, and faculty
<br>Université Paris Descartes
<br>
</div>
</div> 

----

## Sprechstunden (Office Hours)

Während der Vorlesungszeit sind meine Sprechstunden normalerweise :
Mittwochs von 11 bis 13 Uhr. Damit ich es besser organizieren und ein Übersicht über alle Termine zu gewinnen kann, möchte ich Studierende bitten sich für meine Sprechstunde vorher anzumelden. Links für kommende Wochen sind unten zu finden. 

Auf Grund der aktuellen Situation finden alle meine Sprechstunden nur Online statt. Bitte nutzen Sie die Terminplaner Links unten um ein Termin auszumachen. Zu der ausgewählten Zeit, betreten Sie dann bitte mein Virtualen Meeting-Raum: https://tu-dortmund.webex.com/meet/katie.vonholzen.

*Bitte tragen Sie Ihren Namen, Email und Anliegen ein.*
<br>
<br>


**Sprechstunden April 2021**
<br>Donnerstag, 27. April
<br>zwischen 13-15 Uhr
<br>
<br> [Melden Sie sich hier an](https://terminplaner4.dfn.de/VdNx7ffO5qr14vop)

**Sprechstunden Mai 2021**
<br>Mittwochs
<br>zwischen 10-112 Uhr
<br>
<br> [Melden Sie sich hier an](https://terminplaner4.dfn.de/vOpozVkGyNgppTzj)



```{r admin_April, include=FALSE}

# https://terminplaner4.dfn.de/VdNx7ffO5qr14vopUYHKkVPR/admin

```


```{r admin_May, include=FALSE}

# https://terminplaner4.dfn.de/vOpozVkGyNgppTzj49rJ4KJN/admin

```


