---
name: Katie
surname: Von Holzen
position: Akademische Rätin
address: Lehrstuhl Linguistik des Deutschen, Technische Universität Dortmund
www: Kvonholzen.github.io
email: katie.vonholzen@tu-dortmund.de
github: Kvonholzen
twitter: KatieVonHolzen
date: "`r format(Sys.time(), '%B %Y')`"
profilepic: katie_small.png
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)
#library(RefManageR)

# bib <- ReadBib("Publications.bib")
# print(bib)

```


# Education

```{r}
tribble(
  ~Year, ~Degree, ~blank1, ~Institution,
  2013, "Dr. rer. nat. Psychology, magna cum laude", "", "Georg-August-Universität Göttingen, Germany",
  2009, "B.S. Psychology, summa cum laude", "", "University of Wisconsin - Green Bay, USA"
) %>% 
  detailed_entries(Degree, Year, blank1, Institution)


```

# Employment

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Supervisor,
    "Akademische Rätin (Senior Postdoctoral Researcher)", "2019-present", "Technische Universität Dortmund, Germany", "Group Head: Prof. Dr. Sarah Schimke",
    "Postdoctoral Researcher", "2017-2019", "University of Maryland, USA", "Mentor: Prof. Rochelle Newman",
    "Postdoctoral Researcher", "2014-2017", "Université Paris Descartes, France", "Supervisor: Dr. Thierry Nazzi",
    "Scientific Staff", "2010-2013", "Georg-August-Universität Göttingen", "Supervisor: Prof. Dr. Nivedita Mani",
  "Summer Research Intern", "2009", "Dartmouth College, USA", "Supervisor: Prof. Todd Heatherton"
) %>% 
  detailed_entries(Position, Year, Supervisor, Institution)
```


# Research Areas

 * Language acquisition (bilingual and monolingual)
 * Developmental language outcomes
 * Event-Related Potentials (ERPs)
 * Word/wordform recognition
 * Speech segmentation
 * Phono-lexical processing
 * Foreign speech processing
 * Bilingual lexical access
 * Mispronunciation sensitivity
 * Consonant bias in lexical processing
 * Open Science Principles (Open Data, meta-analyses)

# Publications

## Published peer-reviewed papers

```{r}
bibliography_entries("Publications.bib")%>%
   filter(bibtype %in% "Article") %>%
  arrange(desc(year), author)

```

## Chapters in Books

```{r}
bibliography_entries("Publications.bib") %>%
  filter(bibtype %in% "InCollection") %>%
  arrange(desc(year), author)

```

## Peer-Reviewed Conference Proceedings

```{r}
bibliography_entries("Publications.bib") %>%
  filter(bibtype %in% "InProceedings") %>%
  arrange(desc(year), surnames)
```

## Open Data

```{r}
bibliography_entries("Publications.bib") %>%
  filter(bibtype %in% "Misc") %>%
  arrange(desc(year), surnames)
```

## PhD Thesis

```{r}
bibliography_entries("Publications.bib") %>%
  filter(bibtype %in% "PhdThesis") %>%
  arrange(desc(year), surnames)

```


```{r}
## Manuscripts accepted for publication
# bibliography_entries("Publications.bib") %>%
#   filter(bibtype %in% "Article" & year %in% "accepted") %>%
#   arrange(desc(year), surnames)

```

## Manuscripts under revision or review

```{r}
bibliography_entries("Publications.bib") %>%
  filter(bibtype %in% "Unpublished") %>%
  arrange(desc(year), surnames)
```

# Grants

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  "under review", "Initial foreign speech segmentation in school-aged children", "DFG Research Grant, 183,358 €",
    "under review", "Recognition & comprehension of code-switched utterances", "NIH R01 Grant, $27,797",
    2017, "Comparative and Evolutionary Biology of Hearing NIH Postdoctoral Training Grant", "5T32DC00046 – 23",
  2009, "Psi Chi Association of Psychological Science Summer Research Grant ", "$5,000"
) %>% 
  brief_entries(Type, Year, Desc)
```

# Awards

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2019, "Society for Improvement of Psychological Science Mission Award", "For improving psychological science in the face of challenge, as contributor to the ManyBabies1 Collaboration",
  2018, "Berkeley Initiative for Transparency in the Social Sciences (BITSS) Meta-Analysis Challenge Winner", "Shared with co-author Christina Bergmann, $1,000",
  2014, "Summer School Travel Grant: GDR Neurosciences Cognitives du Développement bourses de mobilité à des doctorants", "For the Potsdam Summer School, “Infant Studies on Language Development in Europe (ISOLDE)”",
  2013, "Universitätsbund Göttingen Travel Grant", "For the International Workshop on Bilingualism and Cognitive Control in Krakow, Poland",
  2011, "Paula Menyuk Travel Award", "For BUCLD 2011, $300",
  2010, "Phi Eta Sigma National Honor Society Graduate Scholarship", "$7,000",
  2009, "2nd place Margaret Bernauer Psychology Research Award", "Awarded for Poster Presentation at the Wisconsin Psychological Association Conference, $200"
) %>% 
  brief_entries(Type, Year, Desc)
```

# Invited Talks

```{r}

bibliography_entries("Presentations.bib") %>%
  filter(bibtype == "Booklet") %>%
  filter(str_detect(key, "^i"))%>%
  arrange(desc(year), surnames)

```

# Conference Activity

## Talks Presented

```{r}
bibliography_entries("Presentations.bib") %>%
  filter(bibtype == "Booklet") %>%
  filter(str_detect(key, "^t"))%>%
  arrange(desc(year), surnames)
```

## Posters Presented

```{r}
bibliography_entries("Presentations.bib") %>%
  filter(bibtype == "Booklet") %>%
  filter(str_detect(key, "^p"))%>%
  arrange(desc(year), surnames)
```

# Teaching and Mentorship

## Courses Taught

### Seminars

```{r}

# Alles in allem: Wie bewerten Sie diese Veranstaltung bisher (von 1 'sehr gut' bis 5 'mangelhaft')?

# Intro to Linguistics
# WS 19/20: 2.29
# SoSe 2020: 1.8
# average: 2

# Master Bilingualism
# WS 19/20: 2.24
# SoSe 2020: 2
# average: 2.1



tribble(
  ~Year, ~Course, ~blank1, ~blank2, ~Desc,
  "2019-present", "Zwei Sprachen, ein Gehirn: Bilingualismus und dessen Konsequenzen (Two Languages, One Mind: Bilingualism and its Consequences)", "", "", "Master students",
    "2019-present", "Zwei Sprachen, ein Gehirn: Bilingualismus und dessen Konsequenzen (Two Languages, One Mind: Bilingualism and its Consequences)", "", "", "German Department",
    "2019-present", "Zwei Sprachen, ein Gehirn: Bilingualismus und dessen Konsequenzen (Two Languages, One Mind: Bilingualism and its Consequences)", "", "", "Technische Universität Dortmund",
      "2019-present", "Zwei Sprachen, ein Gehirn: Bilingualismus und dessen Konsequenzen (Two Languages, One Mind: Bilingualism and its Consequences)", "", "", "Average student evaluations' overall grade: 2,1 (German grading system)",
    "2019-present", "Einführung in die Sprachwissenschaft (Introduction to Linguistics)", "", "", "Bachelor students",
    "2019-present", "Einführung in die Sprachwissenschaft (Introduction to Linguistics)", "", "", "German Department",
    "2019-present", "Einführung in die Sprachwissenschaft (Introduction to Linguistics)", "", "", "Technische Universität Dortmund",
      "2019-present", "Einführung in die Sprachwissenschaft (Introduction to Linguistics)", "", "", "Average student evaluations' overall grade: 2 (German grading system)",
    2012, "Language Acquisition and Processing", "", "", "Bachelor students",
    2012, "Language Acquisition and Processing", "", "", "German Department",
    2012, "Language Acquisition and Processing", "", "", "Georg-August-Universität Göttingen"
) %>% 
  detailed_entries(Course, Year, blank1, blank2, Desc)

```

### Lecture-based Courses

```{r}

tribble(
  ~Year, ~Course, ~blank1, ~blank2, ~Desc,
  2018, "Should I Buy That? Comparing Media Claims with Scientific Evidence from Brain & Behavior Research", "", "", "Bachelor students",
    2018, "Should I Buy That? Comparing Media Claims with Scientific Evidence from Brain & Behavior Research", "", "", "Department of Hearing and Speech Sciences",
    2018, "Should I Buy That? Comparing Media Claims with Scientific Evidence from Brain & Behavior Research", "", "", "University of Maryland",
      2018, "Should I Buy That? Comparing Media Claims with Scientific Evidence from Brain & Behavior Research", "", "", "Student evaluations' 'I learned a lot from this course': 3.03 (Disagree - 0 to Strongly Agree (4)",
    2011, "Experimental Methods for Testing Language Comprehension", "", "", "Bachelor students", 
      2011, "Experimental Methods for Testing Language Comprehension", "", "", "German Department", 
      2011, "Experimental Methods for Testing Language Comprehension", "", "", "Georg-August-Universität Göttingen"
) %>% 
  detailed_entries(Course, Year, blank1, blank2, Desc)

```

### Tutorials

```{r}

tribble(
  ~Year, ~Course, ~blank1, ~blank2, ~Desc,
  2017, "Setting up and analyzing an eye-tracking experiment: From Open Sesame to Eyelink to R", "", "", "Doctoral students, postdoctoral researchers, and faculty",
    2017, "Setting up and analyzing an eye-tracking experiment: From Open Sesame to Eyelink to R", "", "", "Université Paris Descartes",
    2017, "Time Course Analysis in R", "", "", "Doctoral students, Research Training Group 2070",
    2017, "Time Course Analysis in R", "", "", "Georg-August-Universität Göttingen",
    2016, "EEG Pre-processing and Analysis Using EEGLAB and ERPLAB", "", "", "Doctoral students, postdoctoral researchers, and faculty",
    2016, "EEG Pre-processing and Analysis Using EEGLAB and ERPLAB", "", "", "Université Paris Descartes"
) %>% 
  detailed_entries(Course, Year, blank1, blank2, Desc)

```

## Students Mentored

### Doctoral students

```{r}

library(tibble)
tribble(
  ~ Person, ~ Year, ~ Title, ~ University,
    "Marie-Christin Flohr", "2020-present", "Child Foreign Speech Processing", "TU Dortmund",
) %>% 
  detailed_entries(Person, Year, University, Title)

```





### Master students

```{r}

library(tibble)
tribble(
  ~ Person, ~ Year, ~ Title, ~ University,
    "Franziska Schlage", "2020-present", "Von Boomer zum Digital Native: Wie der Einfluss fremdsprachlicher Elemente der Jugendsprache in den sozialen Medien die Sprachverarbeitung beeinflusst (From Boomer to Digital Native: How foreign language elements of German youth slang in social media influence language processing)", "TU Dortmund",
      "Judith Boveleth", "2020", "The Difference in the Vocabulary Size of Children with and without Down Syndrome: A Meta-Analysis", "TU Dortmund",
        "Deborah Wolff", "2012", "Segmentierungsfähigkeit von infant- und adult-directed speech bei 11-13 Monate alten Kindern. Eine ERP-Studie. (Segmentation abilities in infant- and adult directed speech in 11-13 month old children: An ERP study)", "Georg-August-Universität Göttingen",
) %>% 
  detailed_entries(Person, Year, University, Title)

```


### Bachelor students

```{r}

library(tibble)
tribble(
  ~ Person, ~ Year, ~ Title, ~ University,
    "Nina Schuster", "2020", "Phonotaktische Segmentierung der L2 – Wie wirken L1-Merkmale deutscher Muttersprachler auf die Segmentierung des Sprachflusses und die Worterkennung in der L2 Englisch ein?. (Phonotactic segmentation in the L2: How do L1 characteristics influence the segmentation and word recognition of the the L2 English speech stream in L1 German learners)", "TU Dortmund",
        "Fabienne Kremer", "2013", "Associating a language with a speaker: Bilingual production is influenced by speaker language", "Georg-August-Universität Göttingen",
) %>% 
  detailed_entries(Person, Year, University, Title)

```

### Internship project students

```{r}

tribble(
  ~Year, ~Project, ~blank, ~People,
  "2017", "French-learning infants' adaptation to a novel accent: The role of consonant/vowel asymmetry", "", "Rosalie Delille (Université Paris Descartes)",  
  "2014-2017", "Consonant and vowel processing in word form segmentation: An infant ERP study", "", "Sofia Carrion, Elisa Moulin, Jeanne Charoy, Marion Lafargue (Université Paris Descartes)",
  "2014-2016", "Emergence of the C-bias during the first year of life: New evidence from own name recognition", "", "Safyya Larinouna, Henry Cheng (Université Paris Descartes") %>% 
  detailed_entries(Project, Year, blank, People)

# - Sofia Carrion, 2017
# - Elisa Moulin, 2015-2016
# - Jeanne Charoy, 2015
# - Marion Lafargue, 2014-2015 

# - Safyya Larinouna, 2016
# - Henry Cheng, 2014 


# *Spoken word perception in L1 and L2: An ERP study of the influence of speaker, gender, frequency, and repetition*, Georg-August-Universität Göttingen, 2012
# - Agniezska Leszczynska

```


### Student project assistantships

```{r}

tribble(
  ~Year, ~Project, ~blank, ~People,
  "2018-2019", "A fast note about slow rate in IDS: Maternal speech rate to preverbal infants facilitates early language development", "", "Sara Cusick, Mary Murphy, Kayla Whitlock, Jennifer Zuhl, Julia Grable, Alexia Proctor (University of Maryland)",  
  "2018-2019", "Utterance alignment of a large, longitudinal corpus in CLAN/CHAT", "", "Heather Wibberley, Taylor Trent, Jillian Doherty, Maggie Roman, Dominique Jenkins, Jessica Mooney (University of Maryland)") %>% 
  detailed_entries(Project, Year, blank, People)

```

# Skills

## Experiment Programming Experience

### Open Sesame/Python

- Intermediate expertise
- Designing experiments, including lexical decision (adults), visual world paradigm (with and without an eye-tracker) and preferential listening (infants)
- Experience advising colleagues on experimental design
- Conducting tutorials with colleagues and students
- Used to promote Open Science practices

### Presentation (Neurobehavioral Systems)

- Intermediate expertise
- Designing experiments, including EEG experiments

### EPrime (Psychology Software Tools, Inc.)

- Beginner expertise
- Designing experiments, including EEG experiments

## Statistical/Data Analysis Experience

### R

- Proficient expertise
- Advising colleagues on statistical analysis, data wrangling
- Conducting tutorials on eye-tracking data
- Growth growth curve modeling (lmer package)
- Mixed effects models (lmer package)
- ANOVA analyses (ez package)
- Producing beautiful graphics (ggplot2 package)
- Analyzing vocabulary data corpora (wordbankr package)
- Power analysis (pwr package)
- Creating RMarkdown files to promote collaboration and accuracy
- Used to promote Open Science practices

### Praat

- Intermediate expertise
- Scripting to automatically analyze sounds (pitch, duration, intensity)
- Stimuli creation
- Interfacing with CLAN output to analyze corpora
- Interfacing with a forced aligner (Easy Align)
- Used to promote Open Science practices

### CHAT/CLAN

- Intermediate expertise
- Analyzing length of utterance
- Time-locking transcripts to audio recordings
- Interfacing with Praat

### EEG/ERPlab

- Intermediate expertise
- Preprocessing EEG data
- Conducting tutorials
- Related MATLAB scripting to automatically analyze EEG/ERP data

### SPSS

- Intermediate expertise
- ANOVA analyses

# Service

## Institutional Service

### TU Dortmund University

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year,
"Manager of the Looking-While-Listening sub-project of ManyBabies-InHome", "2021-present",
     "Executive Board Member of the Department for Language, Literature, and Culture", "2020-present",
  "Committee Member in the founding of the Department for Language, Literature, and Culture", "2020") %>% 
  detailed_entries(Position, Year)

```

### University of Maryland

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year,
    "Member of the Cultural and Linguistic Diversity Committee", 2019,
   "Panel judge for Graduate Research Appreciation Day", 2018
) %>% 
  detailed_entries(Position, Year)
```

### Université Paris Descartes

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year,
    "Co-founder and organizer, Parisian BabyLab Meetings (PaBaLa)", "2014-2017",
   "Co-Chair, Student and Post-doc Talks (SPOT)", "2014-2016"
) %>% 
  detailed_entries(Position, Year)
```

## Professional Service

### Ad-hoc Review

View my [Publons Peer Review Profile](https://publons.com/researcher/1230020/katie-von-holzen/peer-review/)

- Journal of Experimental Child Psychology
- Developmental Science
- Language and Speech
- Infancy
- Bilingualism: Language and Cognition
- Developmental Cognitive Neuroscience
- Child Development
- Journal of Cognitive Psychology
- Journal of Memory and Language


### Conference Review

- International Congress of Infant Studies (ICIS) Conference (2020), Glasgow, UK
- International Association for the Study of Child Language (IASCL) Conference (2020), Philadelphia, PA, USA
- CCERBAL Conference: Bilingual from Birth: Process, Pedagogy and Policy (2016). Ottawa, Canada
- International Workshop on Bilingualism and Cognitive Control (2013). Jagiellonian University, Krakow, Poland
- International Workshop: “Bilingual and Multilingual Interaction” ESRC Centre for Research on Bilingualism (2012), Bangor, Wales

# Professional Memberships

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year,
    "Member of the Deutscher Hochschulverband", "2019-",
   "Member of the International Congress on Infant Studies", "2018-",
  "Member of the National Postdoctoral Association (USA)", "2017-",
  "Member of Women in Cognitive Science (WICS)", "2012-"
) %>% 
  detailed_entries(Position, Year)
```


# Languages

- English, native
- German, fluent (C1)
- French, beginner (A2)


# Community Involvement/Outreach

```{r}
library(tibble)
tribble(
  ~ Place, ~ Year, ~blank1, ~Position,
    "Rosa Parks Elementary School, Hyattsville Education Advisory Committee’s Summer Reading Program", "2018, 2019","", "Volunteer",
   "Winneconne Elementary School, “Being a scientist and living in a foreign country", 2014,"", "Presenter",
  "Preschool Immersion Event, “Bilingual Language Development
at ASC Kinderbewegungshaus”", 2012, "", "Presenter"
) %>% 
  detailed_entries(Place, Year, blank1, Position)
```

