---
name: Katie
surname: Von Holzen
position: "Akademische Rätin"
address: "Lehrstuhl Linguistik des Deutschen, Technische Universität Dortmund"
www: katiemvonholzen.wixsite.com/katievonholzen
email: "katie.m.vonholzen@gmail.com"
github: Kvonholzen
date: "`r format(Sys.time(), '%B %Y')`"
profilepic: katie_pic.jpg
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
library(vitae)
library(scholar)
library(papaja)
```


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Dr. rer. nat. Psychology", "2013", "Georg-August-Universität Göttingen", "Göttingen, Germany",
    "B.S. Psychology, summa cum laude", "2009", "University of Wisconsin - Green Bay", "Green Bay, WI, USA"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# Employment

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Supervisor,
    "Akademische Rätin (Senior Postdoctoral Researcher)", "2019-present", "Technische Universität Dortmund, Germany", "Supervisor: Prof. Dr. Sarah Schimke",
    "Postdoctoral Researcher", "2017-2019", "University of Maryland, USA", "Supervisor: Prof. Rochelle Newman",
    "Postdoctoral Researcher", "2014-2017", "Université Paris Descartes, France", "Supervisor: Dr. Thierry Nazzi",
    "Scientific Staff", "2010-2013", "Georg-August-Universität Göttingen", "Supervisor: Prof. Dr. Nivedita Mani",
  "Summer Research Intern", "2009", "Dartmouth College, USA", "Supervisor: Prof. Todd Heatherton"
) %>% 
  detailed_entries(Position, Year, Institution, Supervisor)
```


# Research Areas

 * Language acquisition (bilingual and monolingual)
 * Developmental language outcomes
 * Event-Related Potentials (ERPs)
 * Word/wordform recognition
 * Speech segmentation
 * Phono-lexical processing
 * Foreign speech processing
 * Bilingual lexical access
 * Mispronunciation sensitivity
 * Consonant bias in lexical processing

# Publications

```{r}
bibliography_entries("Publications.bib")
```

# Peer-Reviewed Conference Proceedings

```{r}
bibliography_entries("Proceedings.bib")
```

# Open Data

```{r}
bibliography_entries("Open_Data.bib")
```

# Manuscripts in Preparation

```{r}
bibliography_entries("Unpublished.bib")
```

# Grants

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2017, "Comparative and Evolutionary Biology of Hearing NIH Postdoctoral Training Grant", "5T32DC00046 – 23",
  2009, "Psi Chi Association of Psychological Science Summer Research Grant ", "$5,000"
) %>% 
  brief_entries(Type, Year, Desc)
```

# Awards

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2019, "Society for Improvement of Psychological Science Mission Award", "For improving psychological science in the face of challenge, as contributor to the ManyBabies1 Collaboration",
  2018, "Berkeley Initiative for Transparency in the Social Sciences (BITSS) Meta-Analysis Challenge Winner", "Shared with co-author Christina Bergmann, $1,000",
  2014, "Summer School Travel Grant: GDR Neurosciences Cognitives du Développement bourses de mobilité à des doctorants", "For the Potsdam Summer School, “Infant Studies on Language Development in Europe (ISOLDE)”",
  2013, "Universitätsbund Göttingen Travel Grant", "For the International Workshop on Bilingualism and Cognitive Control in Krakow, Poland",
  2011, "Paula Menyuk Travel Award", "For BUCLD 2011, $300",
  2010, "Phi Eta Sigma National Honor Society Graduate Scholarship", "$7,000",
  2009, "2nd place Margaret Bernauer Psychology Research Award", "Awarded for Poster Presentation at the Wisconsin Psychological Association Conference, $200"
) %>% 
  brief_entries(Type, Year, Desc)
```

