---
name: Katie
surname: Von Holzen
position: "Lecturer and Researcher"
address: "Bienroder Weg 80, 38106 Braunschweig, Germany"
phone: +49 531 391 8704
profilepic: "./img/katie_headshot.jpg"
www: Kvonholzen.github.io
email: k.von-holzen@tu-braunschweig.de
github: Kvonholzen
twitter: KatieVonHolzen
date: "`r format(Sys.time(), '%B %Y')`"
docname: "Curriculum Vitae"
output:
  vitae::hyndman:
    latex_engine: lualatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

# hyndman

library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)
library(tidyverse)
library(grid)
library(gridExtra)
library(gtable)
#library(RefManageR)

# bib <- ReadBib("Publications.bib")
# print(bib)

```


# Education

```{r}

# needed to add " to get special characters to read in properly
edu_data <- read.csv(file = "data/education.csv", header = T)
#edu_data <- read.csv(file = "data/education.csv", header = T)

edu_data %>%
  detailed_entries(
    what = Degree,
    when = glue::glue("{Start_Year} - {End_Year}"),
    where = Institution,
    with = ""
  )


```


# Employment

```{r}


employ_data <- read.csv(file = "data/employment.csv", header = T)


employ_data %>%
  detailed_entries(
    what = Position,
    when = glue::glue("{Start_Year} - {End_Year}"),
    where = Institution,
    with = Supervisor
  )

```

# Publications

## Published peer-reviewed papers

**Average Impact Factor of 3.4**

```{r}

# apostrophe's need to be given as $'$

`%!in%` <- Negate(`%in%`)

bibliography_entries("data/Publications.bib")%>%
   #filter(type %in% "article-journal") %>%
     filter(type %in% "article-journal" & id %!in% "MB5") %>%
  arrange(desc(issued), author)


```

## Chapters in Books

```{r}
bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "chapter") %>%
  arrange(desc(issued), author)

```

## Peer-Reviewed Conference Proceedings

```{r}
bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "paper-conference") %>%
  arrange(desc(issued), author)
```

## Open Data

```{r}

bibliography_entries("data/Publications.bib") %>%
  filter(id %in% "VonHolzen2021" | id %in% "VonHolzen2022") %>%
  arrange(desc(issued), author)


```

## PhD Thesis

```{r}
bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "thesis") %>%
  arrange(desc(issued), author)

```

```{r}
# 
## Manuscripts accepted pending minor revisions



# bib <- bibliography_entries("data/Publications.bib")
# 
# print(bib)

# bibliography_entries("data/Publications.bib") %>%
#   filter(id %in% "CVaccent")


# bib <- bibliography_entries("data/Publications.bib")
# 
# 
# 
# bibliography_entries("data/Publications.bib") %>%
#   filter(issued %in% "accepted pending minor revisions") %>%
#   arrange(desc(issued), author)

```

```{r}
## Manuscripts accepted for publication
# bibliography_entries("Publications.bib") %>%
#   filter(type %in% "article-journal" & issued %in% "accepted") %>%
#   arrange(desc(issued), author)

```

## Manuscripts under revision or review

```{r}



bibliography_entries("data/Publications.bib")%>%
   #filter(type %in% "article-journal") %>%
     filter(type %in% "article-journal" & id %in% "MB5")

# bibliography_entries("Publications.bib") %>%
#   filter(type %in% "Unpublished") %>%
#   arrange(desc(issued), author)
```


# Grants

```{r}

grant_data <- read.csv(file = "data/grants.csv", header = T)

grant_data <- sapply(grant_data, as.character)
grant_data[is.na(grant_data)] <- " "

grant_data <- as.data.frame(grant_data)

grant_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Funding_Body,
    with = Amount,
    why = Role
  )

```

# Awards

```{r}

awards_data <- read.csv(file = "data/awards.csv", header = T)

awards_data %>%
  detailed_entries(
    what = Name,
    when = Year,
    where = Desc,
    with = Amount
  )

```







## Supervision/Mentorship


```{r}

student_data <- read.csv(file = "data/students.csv", header = T)

student_data <- sapply(student_data, as.character)
student_data[is.na(student_data)] <- " "

student_data <- as.data.frame(student_data)

```

### Postdoctoral researchers

```{r}

postdoc_data <- subset(student_data, Type == "Postdoctoral Researcher")


postdoc_data %>%
  detailed_entries(
    what = Person,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Title,
    with = Institution
  )


```

### Doctoral students

```{r}

phd_data <- subset(student_data, Type == "PhD")


phd_data %>%
  detailed_entries(
    what = Person,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Title,
    with = Institution
  )


```

### Master students

```{r}

master_data <- subset(student_data, Type == "Master")


master_data %>%
  detailed_entries(
    what = Person,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Title,
    with = Institution
  )


```


### Bachelor students

```{r}

bachelor_data <- subset(student_data, Type == "Bachelor")


bachelor_data %>%
  detailed_entries(
    what = Person,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Title,
    with = Institution
  )

```

### Internships and project assistantships

```{r}

intern_data <- subset(student_data, Type == "Intern")

intern_data %>%
  detailed_entries(
    what = Title,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Person,
    with = Institution
  )


# - Sofia Carrion, 2017
# - Elisa Moulin, 2015-2016
# - Jeanne Charoy, 2015
# - Marion Lafargue, 2014-2015 

# - Safyya Larinouna, 2016
# - Henry Cheng, 2014 


# *Spoken word perception in L1 and L2: An ERP study of the influence of speaker, gender, frequency, and repetition*, Georg-August-Universität Göttingen, 2012
# - Agniezska Leszczynska

```




# Languages

- English, native
- German, fluent (C1)
- French, beginner (A2)









