---
name: Katie
surname: Von Holzen
position: "Akademische Rätin"
address: "Emil-Figge Str. 50, 44227 Dortmund, Germany, Tel: (+49)231 755-2850"
profilepic: "./img/katie_headshot.jpg"
www: Kvonholzen.github.io
email: katie.vonholzen@tu-dortmund.de
github: Kvonholzen
twitter: KatieVonHolzen
date: "`r format(Sys.time(), '%B %Y')`"
docname: "Curriculum Vitae"
output: vitae::hyndman

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

current_dir <- getwd()
current_dir <- gsub("specialized_CVs/Aachen_DevPsych", "", current_dir)

knitr::opts_knit$set(root.dir = current_dir)


# hyndman

library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)
library(tidyverse)
library(grid)
library(gridExtra)
library(gtable)
#library(RefManageR)

# bib <- ReadBib("Publications.bib")
# print(bib)

```


# Education

```{r}

edu_data <- read.csv(file = "data/education.csv", header = T)

edu_data %>%
  detailed_entries(
    what = Degree,
    when = glue::glue("{Start_Year} - {End_Year}"),
    where = Institution,
    with = ""
  )


```


# Employment

```{r}


employ_data <- read.csv(file = "data/employment.csv", header = T)


employ_data %>%
  detailed_entries(
    what = Position,
    when = glue::glue("{Start_Year} - {End_Year}"),
    where = Institution,
    with = Supervisor
  )

```

# Research Areas


```{r}

research_area <- read.csv(file = "data/research_areas.csv", header = T)

research_area <- research_area %>%
  group_by(area) %>%
  dplyr::mutate(detail_list = paste0(detail, collapse = "; "))

research_area <- unique(research_area[,c("area", "detail_list")])


research_area %>%
  detailed_entries(
    what = detail_list,
    when = area
  )



```




# Invited Talks


```{r}

bibliography_entries("data/Presentations.bib") %>%
  filter(str_detect(id, "^i"))%>%
  arrange(desc(issued), author)

```





# Conference Activity


## Talks Presented


```{r}
bibliography_entries("data/Presentations.bib") %>%
  filter(str_detect(id, "^t"))%>%
  arrange(desc(issued), author)
```


## Posters Presented

```{r}
bibliography_entries("data/Presentations.bib") %>%
  filter(str_detect(id, "^p"))%>%
  arrange(desc(issued), author)
```


# Teaching and Mentorship


## Courses Taught


```{r}

teaching_data <- read.csv(file = "data/teaching.csv", header = T)


teaching_data <- sapply(teaching_data, as.character)
teaching_data[is.na(teaching_data)] <- " "

teaching_data <- as.data.frame(teaching_data)


```


### Seminars


```{r}

seminar_data <- subset(teaching_data, Type == "Seminar")


seminar_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Desc,
    with = "",
    why = Evaluation
  )

```


### Lecture-based Courses

```{r}

lecture_data <- subset(teaching_data, Type == "Lecture")

lecture_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Desc,
    with = "",
    why = Evaluation
  )

```


### Tutorials

*I've written a suite of Tutorials available on my website (https://kvonholzen.github.io/Tutorials.html) for creating experiments in Open Sesame, analyzing data in R, working in Praat, and preprocessing EEG/ERP data in EEGlab/ERPlab. I've also created a tutorial for analyzing eyetracking data with R (https://bookdown.org/katie_m_vonholzen/Eyetracking_Statistical_Analysis_Tutorial/)*

```{r}

tutorial_data <- subset(teaching_data, Type == "Tutorial")


tutorial_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    with = "",
    why = Desc
  )

```


## Students Mentored


```{r}

student_data <- read.csv(file = "data/students.csv", header = T)

student_data <- sapply(student_data, as.character)
student_data[is.na(student_data)] <- " "

student_data <- as.data.frame(student_data)

```

### Doctoral students

```{r}

phd_data <- subset(student_data, Type == "PhD")


phd_data %>%
  detailed_entries(
    what = Title,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Person,
    with = Institution
  )


```

### Master students

```{r}

master_data <- subset(student_data, Type == "Master")


master_data %>%
  detailed_entries(
    what = Title,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Person,
    with = Institution
  )


```


### Bachelor students

```{r}

bachelor_data <- subset(student_data, Type == "Bachelor")


bachelor_data %>%
  detailed_entries(
    what = Title,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Person,
    with = Institution
  )

```

### Internships and project assistantships

```{r}

intern_data <- subset(student_data, Type == "Intern")

intern_data %>%
  detailed_entries(
    what = Title,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Person,
    with = Institution
  )


# - Sofia Carrion, 2017
# - Elisa Moulin, 2015-2016
# - Jeanne Charoy, 2015
# - Marion Lafargue, 2014-2015 

# - Safyya Larinouna, 2016
# - Henry Cheng, 2014 


# *Spoken word perception in L1 and L2: An ERP study of the influence of speaker, gender, frequency, and repetition*, Georg-August-Universität Göttingen, 2012
# - Agniezska Leszczynska

```


# Skills

## Experiment Programming Experience

```{r}

experiment_prog <- read.csv(file = "data/skills.csv", header = T)

experiment_prog <- subset(experiment_prog, skill == "experiment_programming")

experiment_prog <- experiment_prog %>%
  group_by(program) %>%
  dplyr::mutate(detail_list = paste0(detail, collapse = "; "))

experiment_prog <- unique(experiment_prog[,c("program", "expertise", "detail_list")])


experiment_prog %>%
  detailed_entries(
    what = expertise,
    when = program,
    where = detail_list,
    with = ""
  )


```


## Statistical/Data Analysis Experience

```{r}

stats_an <- read.csv(file = "data/skills.csv", header = T)

stats_an <- subset(stats_an, skill == "stats_analysis")

stats_an <- stats_an %>%
  group_by(program) %>%
  dplyr::mutate(detail_list = paste0(detail, collapse = "; "))

stats_an <- unique(stats_an[,c("program", "expertise", "detail_list")])


stats_an %>%
  detailed_entries(
    what = expertise,
    when = program,
    where = detail_list,
    with = ""
  )


```



# Service

## Institutional Service

```{r}

inst_service <- read.csv(file = "data/service.csv", header = T)

inst_service <- sapply(inst_service, as.character)
inst_service[is.na(inst_service)] <- " "

inst_service <- as.data.frame(inst_service)


inst_service %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Institution,
    with = ""
  )


```

## Professional Service

For a complete record of my peer-review service, view my Publons Peer Review Profile (https://publons.com/researcher/1230020/katie-von-holzen/peer-review/)


```{r}
### Conference Review
# 
# - International Congress of Infant Studies (ICIS) Conference (2020), Glasgow, UK
# - International Association for the Study of Child Language (IASCL) Conference (2020), Philadelphia, PA, USA
# - CCERBAL Conference: Bilingual from Birth: Process, Pedagogy and Policy (2016). Ottawa, Canada
# - International Workshop on Bilingualism and Cognitive Control (2013). Jagiellonian University, Krakow, Poland
# - International Workshop: “Bilingual and Multilingual Interaction” ESRC Centre for Research on Bilingualism (2012), Bangor, Wales

```



# Professional Memberships

```{r}

prof_member <- read.csv(file = "data/memberships.csv", header = T)

prof_member %>%
  brief_entries(
    what = Name,
    when = glue::glue("{Start_Year} - {End_Year}"))


```


# Languages

- English, native
- German, fluent (C1)
- French, beginner (A2)



# Community Involvement/Outreach

```{r}

community <- read.csv(file = "data/community.csv", header = T)

community <- sapply(community, as.character)
community[is.na(community)] <- " "

community <- as.data.frame(community)

community %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Role,
    with = ""
  )

```


