---
name: Katie
surname: Von Holzen
position: "Lecturer and Researcher"
address: "Bienroder Weg 80, 38106 Braunschweig, Germany"
profilepic: "./img/katie_headshot.jpg"
www: Kvonholzen.github.io
email: katie.m.vonholzen@gmail.com
github: Kvonholzen
twitter: KatieVonHolzen
date: "`r format(Sys.time(), '%B %Y')`"
docname: "Curriculum Vitae"
output:
  vitae::hyndman:
    latex_engine: lualatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

# hyndman

library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)
library(tidyverse)
library(grid)
library(gridExtra)
library(gtable)
#library(RefManageR)

# bib <- ReadBib("Publications.bib")
# print(bib)

```


# Employment

```{r}


employ_data <- read.csv(file = "data/employment.csv", header = T)
# 
# employ_data <- read.csv(file = "data/employment.csv", header = T, encoding = "UTF-8"

employ_data %>%
  detailed_entries(
    what = Position,
    when = glue::glue("{Start_Year} - {End_Year}"),
    where = Institution,
    with = Supervisor
  )

```

# Open Science Experience

## Open Data

```{r}

bibliography_entries("data/Publications.bib") %>%
  filter(id %in% "VonHolzen2021" | id %in% "VonHolzen2022") %>%
  arrange(desc(issued), author)


```



## Preregistrations

* Ini-Seg: Phonotactics
    + https://osf.io/58bhv/?view_only=d48e6184241f4c77b5cb1ce20c98e2d7
* Ini-Seg: Lexical Transparency
    + https://osf.io/dsg57/?view_only=b0ee304b3b0941ffa6e64ce0abc3b193
* The influence of sentence frames in an online (remote) word comprehension experiment
    + https://osf.io/7dpqg/?view_only=620d69ba96d24e4892bcfe351dc3a406
* The role of speech register in foreign word learning
    + https://osf.io/5g2bz/?view_only=5ed0e404a83746cd906a4720232e3d3e




## Talks

* How to integrate open science into language acquisition research
    + Presented at colloquiums at the TU Braunschweig, TU Dortmund, and University of Maryland

## Within ManyBabies

* Open Handbook for ManyBabies - AtHome: Hand Annotation
    + https://osf.io/axtqr/?view_only=8aaeac0683f34bcdb6acfd2aa2309bc0
* Draft of stimuli selection procedure for the ManyBabies - AtHome LWL Team
    + https://kvonholzen.github.io/MBAH_LWL.html


# Grants

```{r}

grant_data <- read.csv(file = "data/grants.csv", header = T)

grant_data <- sapply(grant_data, as.character)
grant_data[is.na(grant_data)] <- " "

grant_data <- as.data.frame(grant_data)

grant_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Funding_Body,
    with = Amount,
    why = Role
  )

```

# Awards

```{r}

awards_data <- read.csv(file = "data/awards.csv", header = T)

awards_data %>%
  detailed_entries(
    what = Name,
    when = Year,
    where = Desc,
    with = Amount
  )

```


# Education

```{r}

# needed to add ", encoding = "UTF-8" to get special characters to read in properly
edu_data <- read.csv(file = "data/education.csv", header = T)

edu_data %>%
  detailed_entries(
    what = Degree,
    when = glue::glue("{Start_Year} - {End_Year}"),
    where = Institution,
    with = ""
  )


```



# Selected Publications

For a complete list, visit my [ORCID profile](https://orcid.org/0000-0001-7636-2209)

```{r}

# apostrophe's need to be given as $'$

`%!in%` <- Negate(`%in%`)

bibliography_entries("data/Publications.bib")%>%
   #filter(type %in% "article-journal") %>%
     filter(type %in% "article-journal" & id %!in% "MB5") %>%
            filter(id %in% "CVaccent" | id %in% "MetaAnalysis" | id %in% "MB1") %>%
  arrange(desc(issued), author)


```

## Manuscripts under revision or review

```{r}



bibliography_entries("data/Publications.bib")%>%
   #filter(type %in% "article-journal") %>%
     filter(type %in% "article-journal" & id %in% "MB5")

# bibliography_entries("Publications.bib") %>%
#   filter(type %in% "Unpublished") %>%
#   arrange(desc(issued), author)

```



# Teaching and Mentorship

```{r}

teaching_data <- read.csv(file = "data/teaching.csv", header = T)

```


## Tutorials

*I've written a suite of Tutorials available on my website (https://kvonholzen.github.io/Tutorials.html) for creating experiments in Open Sesame, analyzing data in R, working in Praat, and preprocessing EEG/ERP data in EEGlab/ERPlab. I've also created a tutorial for analyzing eyetracking data with R (https://bookdown.org/katie_m_vonholzen/Eyetracking_Statistical_Analysis_Tutorial/)*

```{r}

tutorial_data <- subset(teaching_data, Type == "Tutorial")

tutorial_data$End_Year <- ""

tutorial_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = "",
    with = "",
    why = Desc
  )



```

## Courses Taught


```{r}


teaching_data <- sapply(teaching_data, as.character)
teaching_data[is.na(teaching_data)] <- " "

teaching_data <- as.data.frame(teaching_data)


```


### Seminars


```{r}

seminar_data <- subset(teaching_data, Type == "Seminar")


seminar_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Desc,
    with = "",
    why = Evaluation
  )

```


### Lecture-based Courses

```{r}

lecture_data <- subset(teaching_data, Type == "Lecture")

lecture_data %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Desc,
    with = "",
    why = Evaluation
  )

```



## Current Students


```{r}

student_data <- read.csv(file = "data/students.csv", header = T)

student_data <- sapply(student_data, as.character)
student_data[is.na(student_data)] <- " "

student_data <- as.data.frame(student_data)

```

### Postdoctoral researchers

```{r}

postdoc_data <- subset(student_data, Type == "Postdoctoral Researcher")


postdoc_data %>%
  detailed_entries(
    what = Person,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Title,
    with = Institution
  )


```

### Doctoral students

```{r}

phd_data <- subset(student_data, Type == "PhD")


phd_data %>%
  detailed_entries(
    what = Person,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Title,
    with = Institution
  )


```



# Invited Talks and Conference Activity

## Selected Invited Talks


```{r}

bibliography_entries("data/Presentations.bib") %>%
  filter(str_detect(id, "^i"))%>%
  filter(id %in% "iVH2022c" | id %in% "iVH2021" | id %in% "iVH2020" | id %in% "iVH2019a") %>%
  arrange(desc(issued), author)


```


## Selected Conference Talks


```{r}
bibliography_entries("data/Presentations.bib") %>%
  filter(str_detect(id, "^t"))%>%
    filter(id %in% "tV2022a" | id %in% "tV2022b" | id %in% "tB2021" | id %in% "tVH2019" | id %in% "tVH2018b") %>%
  arrange(desc(issued), author)

```



## Selected Conference Posters


```{r}

bibliography_entries("data/Presentations.bib") %>%
  filter(str_detect(id, "^p"))%>%
  filter(id %in% "pVH2022a" | id %in% "pVH2018a" | id %in% "pVH2017c") %>%
  arrange(desc(issued), author)

```




# Skills

## Experiment Programming Experience

```{r}

experiment_prog <- read.csv(file = "data/skills.csv", header = T)

experiment_prog <- subset(experiment_prog, skill == "experiment_programming")

experiment_prog <- experiment_prog %>%
  group_by(program) %>%
  dplyr::mutate(detail_list = paste0(detail, collapse = "; "))

experiment_prog <- unique(experiment_prog[,c("program", "expertise", "detail_list")])


experiment_prog %>%
  detailed_entries(
    what = expertise,
    when = program,
    where = detail_list,
    with = ""
  )


```


## Statistical/Data Analysis Experience

```{r}

stats_an <- read.csv(file = "data/skills.csv", header = T)

stats_an <- subset(stats_an, skill == "stats_analysis")

stats_an <- stats_an %>%
  group_by(program) %>%
  dplyr::mutate(detail_list = paste0(detail, collapse = "; "))

stats_an <- unique(stats_an[,c("program", "expertise", "detail_list")])


stats_an %>%
  detailed_entries(
    what = expertise,
    when = program,
    where = detail_list,
    with = ""
  )


```



# Service

## Institutional Service

```{r}

inst_service <- read.csv(file = "data/service.csv", header = T)

inst_service <- sapply(inst_service, as.character)
inst_service[is.na(inst_service)] <- " "

inst_service <- as.data.frame(inst_service)


inst_service %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Institution,
    with = ""
  )


```

## Professional Service

For a complete record of my peer-review service, view my Publons Peer Review Profile (https://www.webofscience.com/wos/author/record/1483321)


```{r}
### Conference Review
# 
# - International Congress of Infant Studies (ICIS) Conference (2020), Glasgow, UK
# - International Association for the Study of Child Language (IASCL) Conference (2020), Philadelphia, PA, USA
# - CCERBAL Conference: Bilingual from Birth: Process, Pedagogy and Policy (2016). Ottawa, Canada
# - International Workshop on Bilingualism and Cognitive Control (2013). Jagiellonian University, Krakow, Poland
# - International Workshop: “Bilingual and Multilingual Interaction” ESRC Centre for Research on Bilingualism (2012), Bangor, Wales

```



# Professional Memberships

```{r}

prof_member <- read.csv(file = "data/memberships.csv", header = T)

prof_member %>%
  brief_entries(
    what = Name,
    when = glue::glue("{Start_Year} - {End_Year}"))


```


# Languages

- English, native
- German, fluent (C1)
- French, beginner (A2)



# Community Involvement/Outreach

```{r}

community <- read.csv(file = "data/community.csv", header = T)

community <- sapply(community, as.character)
community[is.na(community)] <- " "

community <- as.data.frame(community)

community %>%
  detailed_entries(
    what = Name,
    when = glue::glue("{Start_Year}{End_Year}"),
    where = Role,
    with = ""
  )

```






