---
name: Katie
surname: Von Holzen
position: "Lecturer and Researcher"
address: "Hagenring 22, 38106 Braunschweig, Germany"
profilepic: "./img/katie_headshot.jpg"
www: Kvonholzen.github.io
email: katie.m.vonholzen@gmail.com
github: Kvonholzen
twitter: KatieVonHolzen
date: "`r format(Sys.time(), '%B %Y')`"
docname: "Publications List"
output:
  vitae::hyndman:
    latex_engine: lualatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

# hyndman

library(vitae)
library(scholar)
library(papaja)
library(tibble)
library(stringr)
library(tidyverse)
library(grid)
library(gridExtra)
library(gtable)
#library(RefManageR)

# bib <- ReadBib("Publications.bib")
# print(bib)

```


# Published peer-reviewed papers

**Average Impact Factor of 3.4**

```{r}

# apostrophe's need to be given as $'$

bibliography_entries("data/Publications.bib")%>%
   #filter(type %in% "article-journal") %>%
     filter(type %in% "article-journal") %>%
  filter(id != "MB5" & id != "AdultIDSADS") %>%
  arrange(desc(issued), author)


```

# Manuscripts under revision or review (peer-reviewed)

```{r}



bibliography_entries("data/Publications.bib")%>%
   #filter(type %in% "article-journal") %>%
     filter(type %in% "article-journal" & id %in% "MB5" | type %in% "article-journal" & id %in% "AdultIDSADS")

# bibliography_entries("Publications.bib") %>%
#   filter(type %in% "Unpublished") %>%
#   arrange(desc(issued), author)
```

# Peer-Reviewed Conference Proceedings

```{r}
bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "paper-conference") %>%
  arrange(desc(issued), author)
```

# Chapters in Books

```{r}
bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "chapter") %>%
  arrange(desc(issued), author)

```

# Open Data

```{r}

bibliography_entries("data/Publications.bib") %>%
  filter(id %in% "VonHolzen2021" | id %in% "VonHolzen2022") %>%
  arrange(desc(issued), author)


```

# Preregistrations

* Ini-Seg: Phonotactics
    + https://osf.io/58bhv/?view_only=d48e6184241f4c77b5cb1ce20c98e2d7
* Ini-Seg: Lexical Transparency
    + https://osf.io/dsg57/?view_only=b0ee304b3b0941ffa6e64ce0abc3b193
* The influence of sentence frames in an online (remote) word comprehension experiment
    + https://osf.io/7dpqg/?view_only=620d69ba96d24e4892bcfe351dc3a406
* The role of speech register in foreign word learning
    + https://osf.io/5g2bz/?view_only=5ed0e404a83746cd906a4720232e3d3e


# PhD Thesis

```{r}
bibliography_entries("data/Publications.bib") %>%
  filter(type %in% "thesis") %>%
  arrange(desc(issued), author)

```

```{r}
# 
## Manuscripts accepted pending minor revisions



# bib <- bibliography_entries("data/Publications.bib")
# 
# print(bib)

# bibliography_entries("data/Publications.bib") %>%
#   filter(id %in% "CVaccent")


# bib <- bibliography_entries("data/Publications.bib")
# 
# 
# 
# bibliography_entries("data/Publications.bib") %>%
#   filter(issued %in% "accepted pending minor revisions") %>%
#   arrange(desc(issued), author)

```

```{r}
## Manuscripts accepted for publication
# bibliography_entries("Publications.bib") %>%
#   filter(type %in% "article-journal" & issued %in% "accepted") %>%
#   arrange(desc(issued), author)

```



